---
title: "Reproducible Research: Peer Assessment 1"
output: 
  html_document:
    keep_md: true
---

## Loading and preprocessing the data

The Following code load the data from the activity.csv and process the data

```{r processdata}

data <- read.csv('activity.csv')
data$date <- as.Date(data$date)

```


## What is mean total number of steps taken per day?

1.Histogram of Total Number of Steps taken per day ignoring NA values:

```{r plot_hist}

new_data <- data[!is.na(data$steps),]
agg <- aggregate(steps~date,new_data,sum)
hist(agg$steps,col='red',breaks=10,main="Histogram Of Steps",xlab='Total Steps Taken Each Day')

```

2.The Calculations of Mean and Median :

```{r calcmean}
men <- mean(agg$steps)
med <- median(agg$steps)
cat('Mean is ',men,'and Median is ',med)

```


## What is the average daily activity pattern?

1.Time series plot of the 5-minute interval (x-axis) and the average number of steps taken, averaged across all days (y-axis) :

```{r timeseries}

agg2 <- aggregate(steps~interval,new_data,mean)
plot(agg2$interval,agg2$steps,type='l',col='blue',xlab='Interval',ylab='Average Steps per Interval')

```

2.The 5-minute interval with max value ageraged over days :

```{r}
maxint <- agg2$interval[which.max(agg2$steps)]
cat('The 5-minute interval having maximum steps averaged accross all days is',maxint )

```


## Inputing missing values

1. Total number of missing values in the dataset :
```{r missingval}
mval <- sum(is.na(data$steps))
cat('Total number of missing values in the dataset is ', mval)
```

2&3. Missing data is filled in by the mean of the corresponding interval accross the days.

```{r filldata}

meanval <- data.frame(round(agg2$steps),row.names=agg2$interval)
len <- dim(data)[1]
for(i in 1:len)
{
    if(is.na(data$steps[i]))
    {
        data$steps[i] <- meanval[as.character(data$interval[i]),1]
    }
}
```

4. Histogram of steps with mean and median.
```{r newhist}

agg <- aggregate(steps~date,data,sum)
hist(agg$steps,col='green',breaks=10,main="Histogram Of Steps",xlab='Total Steps Taken Each Day')
men <- mean(agg$steps)
med <- median(agg$steps)
cat('Mean  is ',men,'and Median is ',med)

```


## Are there differences in activity patterns between weekdays and weekends?
