---
title: "Reproducible Research: Peer Assessment 1"
output: 
  html_document:
    keep_md: true
---

## Loading and preprocessing the data

The Following code load the data from the activity.csv and process the data

```{r processdata}

data <- read.csv('activity.csv')
data$date <- as.Date(data$date)

```


## What is mean total number of steps taken per day?

Histogram of Total Number of Steps taken per day ignoring NA values is as below

```{r plot_hist}

new_data <- data[!is.na(data$steps),]
agg <- aggregate(steps~date,new_data,sum)
hist(agg$steps,col='red',breaks=10,main="Histogram Of Steps",xlab='Total Steps Taken Each Day')
men <- mean(agg$steps)
med <- median(agg$steps)
cat('Mean is ',men,'and Median is ',med)

```


## What is the average daily activity pattern?

Time series plot of the 5-minute interval (x-axis) and the average number of steps taken, averaged across all days (y-axis) is as below :

```{r timeseries}

agg2 <- aggregate(steps~interval,new_data,mean)
plot(agg2$interval,agg2$steps,type='l',col='blue',xlab='Interval',ylab='Average Steps per Interval')
maxint <- agg2$interval[which.max(agg2$steps)]
cat('The 5-minute interval having maximum steps averaged accross all days is',maxint )

```



## Imputing missing values



## Are there differences in activity patterns between weekdays and weekends?
